A Novel Approach to Supervised Classification Using Non-Linear Metrics

### 2017-01-20 icml2017/paper.tex
add

\clearpage
\section{Numerical Experiments/Results}

@@

In the experiment we took MNIST and CIFAR100 dataset

we used  auto-encoders and then run Algorithm XXX

Cifra 
[7, 35, 64, 71, 73, 81]

@@

MNIST
[120]

@@

In Figure \ref{fig:AE}
\begin{figure}

\todo[inline,color=green]{TODO}
\caption{TODO}
\label{fig:AE}

\subsection{NN comparison}

@@

In Figure \ref{fig:NN-exp}
\begin{figure}

@@

\begin{table}
\caption{Comparison of testing error of NN with different metrics.}
\label{tbl:BD-NN}
\begin{tabular}{l|r|r|r|r}
dataset & NN-$\ell_1$ 
		& NN-$\ell_2$
		& NN-$\ell_\infty$
        & NN-B
\\        
a1a
\\
a9a
\\
covtype
\\
mushrooms
\\
splice
\\
iris
\\
breast-cancer
\end{tabular}

@@

>>>>

try the approach suggested today.
Use a subset of data, find $B$, 
compute $R^{-1}$ and remove values on the left from knee point
and then we should get points on bounday and re-optimize.

why our approach is better for proposing where to sample, we can also use KNN

\clearpage
\onecolumn 
\section{Numerical Experiments/Results}

@@

In the experiment we took MNIST and CIFAR100 dataset.
\begin{itemize}
\item We run autoencoders with CNN to 
find a condensed representation of images
\item after we find the best $B$ and get a collection of outliers
\item We show both examples for a non-outlier case and also for outlier case
\end{itemize}

In Figure \ref{fig:AE-MNIST}
(left) we show an non-outlier image together with 4 closest points.
On right, we show an outlier image together with 4 it's closest neighbours.
We compare it with the non-optimized distance metric (second row). The detailed description of the experiment is in supplementary material.
\begin{figure}[h!]

\todo[inline,color=green]{TODO}
\caption{TODO}
\label{fig:AE-MNIST}

In Figure \eqref{fig:AE-CIFAR}
we show the same but on CIFAR100 dataset.
The detailed description of the experiment is in supplementary material.
\begin{figure}[h!]

\todo[inline,color=green]{TODO}
\caption{TODO}
\label{fig:AE-CIFAR}

@@

@@

\clearpage
\subsection{NN comparison}

@@

In Figure \ref{fig:NN-exp}
\begin{figure}[h!]

@@

\begin{table}[h!]
\caption{Comparison of testing error of NN with different metrics.}
\label{tbl:BD-NN}
\begin{tabular}{l|r|r|r|r}
dataset & NN-$\ell_1$ 
		& NN-$\ell_2$
		& NN-$\ell_\infty$
        & NN-B
\\        
a1a
\\
a9a
\\
covtype
\\
mushrooms
\\
splice
\\
iris
\\
breast-cancer
\end{tabular}

@@

\clearpage
